Layered Formal Verification of an Industrial TCP/IP Stack

### 2021-06-02 SecDev21/paper.tex
finishing the KLEE part

Symbolic execution is a means of executing programs with symbolic values rather than concrete values \cite{symbolic_exec_survey:2018}. Exhaustive symbolic execution can be considered sound and complete (it prevents false negatives and false positives), and thus, it is suitable for formal verification. In \cite{vanoverberghe2008using}, the authors present how symbolic execution can be used to improve deductive verification, and in \cite{kassios2012comparing} the authors demonstrated the technique's value in inferring contracts. For our work,  the KLEE\footnote{\url{https://klee.github.io}} symbolic execution engine has been used. KLEE is built upon the LLVM optimizer's bytecode, and it offers a very simple yet powerful C interface.

@@

\todo[inline]{KG: fixed up to here}

We want to prove that the C code implementation of the respects rules extracted from RFC 793. To achieve this, symbolic execution is used to verify that all the possible paths when executing the \spark{tcpProcessSegment} function will result in a state that respects the RFC 793 rules. This process requires three steps, that are show in \Cref{code:kleedriver}. A symbolic incoming segment is created in the first lines to allow us to account for all possible incoming segments. Then at \cref{code:kleedriver:tcpProcessSegment} the function \texttt{tcpProcessSegment} is executed symbolically with KLEE. Finally, it is followed at \cref{code:kleedriver:assert} by a call to \texttt{klee\_assert} that checks if the code leads to a valid state identified in the protocol’s specification.

Once the \texttt{klee\_assert} is validated by KLEE, which means that the code respects the RFC 793 specification, it can be copied out as a valid SPARK contract for the function \spark{TCP_Process_One_Segment}. With this step done, the concurrency challenge has been solved and the function \spark{TCP_Wait_For_Events} has a correct and an accurate contract, which makes possible the verification of the functional correctness of the TCP user
functions thanks to SPARK.

\section{Hardening the user's API}
\label{sec:API}

>>>>

Symbolic execution is a means of executing programs with symbolic values rather than concrete values \cite{symbolic_exec_survey:2018}. Exhaustive symbolic execution can be considered sound and complete (it prevents false negatives and false positives), and thus, it is complementary to formal verification. In \cite{vanoverberghe2008using}, the authors present how symbolic execution can be used to improve deductive verification, and in \cite{kassios2012comparing} the authors demonstrated the technique's value in inferring contracts. For our work, the KLEE\footnote{\url{https://klee.github.io}} symbolic execution engine is used. KLEE is built upon the LLVM optimizer's bytecode, and it offers a very simple yet powerful C interface.

@@

Symbolic execution is used to verify that all the possible paths when executing the \spark{tcpProcessSegment} function will result in a state that respects the RFC 793 extracted specifications. This process requires three steps shown in \Cref{code:kleedriver}. Firstly, a symbolic incoming segment is created, allowing to account for all possible incoming segments (see lines 1-4). Then at \cref{code:kleedriver:tcpProcessSegment}, function \texttt{tcpProcessSegment} is executed symbolically by KLEE. Finally, the assertion, \texttt{klee\_assert}, at \cref{code:kleedriver:assert} checks if the code leads to a valid state, one that is within the protocol's specification. If there is no raised assertion, then the contract represented by the assertion is deemed proved, and the relevant C code respects the protocol's specification regarding that contract. The assertion is then converted to a SPARK contract and added to the function \spark{TCP_Process_One_Segment}. This enables the SPARK prover to reason about the possible side-effects caused by the C-code on the state of a TCP connection and thus, enables the functional correctness verification of the TCP user functions.

\todo[inline]{KG: fixed up to here}
\section{Hardening the user's API}
\label{sec:API}
